Analyzing Income Inequality Trends in the United States: Impacts of the COVID-19 Pandemic and Policy Implications

### 2024-11-28 paper/paper.qmd
Update paper.qmd

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

>>>>

Income inequality is a pressing issue not only in the United States but also globally. It pertains to the uneven distribution of income across a population, spotlighting disparities in financial well-being. Unlike wealth, which accounts for assets such as homes and stocks, income inequality focuses on earnings from various sources—wages, salaries, interest from savings, stock dividends, rental income, and profits from selling assets at a higher price than their purchase cost. This distinction is crucial for understanding the different facets of economic inequality. Therefore understanding inequality may provide insights for policymakers or researchers in contributing the problem.

This paper aims to investigate the dynamics of income inequality in the United States, especially focusing on the period from 2002 to 2019. Using the dataset provided by United States Census and World Inequality Database (WID), we will fully investigate income trends across the social class, top 1%, top 10% and bottom 50% of income inequality. Moreover, will be considering variables such as year, social class, and race to find out the correlation between these factors.

Even though researchers has studied on income inequality in the United States, there are still remaining income gap between individual firms who are living in the United States. To efficiently investigate this income gap, our paper would focus on exploring datasets and multiple linear regression modeling to find out the full details (trends, patterns) about income inequality that is occurring in the United States.

The paper is structured as following: Section 2 introduces the data used for analysis and findings, including the variables of interest. Section 3 introduces the linear regression model to examine the correlation between time (year) and social class to investigate income inequality in the United States. Section 4 introduces the full analysis of the table which will include the summary. Section 5 may discuss about the findings that we investigated and also talk about the weaknesses of this paper and its next steps.
